Final Report

### 2022-05-06 Final Report.Rmd
changed decimals on y-axis

@@

#Percentage of those affected 
affected_high<- joined_high %>% 
  mutate(percent_high = total_deaths/mean(Count))

@@

affected_low <- joined_low %>% 
  mutate(percent_low = total_deaths/mean(Count))

>>>>

In order to get rid of the leading zeros, and clean up the y-axis, we multiplied the 'percent_high' and 'percent_low' calculation by 10,000,000

@@

#Percentage of those affected 
affected_high<- joined_high %>% 
  mutate(percent_high = (total_deaths/mean(Count))*(1000000))

@@

affected_low <- joined_low %>% 
  mutate(percent_low = (total_deaths/mean(Count))*(1000000))
